\large How resource abundance and stochasticity affect animals' space-use requirements

### 2023-09-17 writing/appendix-3-empirical-modeling.Rmd
added AIC comparison with mu-only model

Finally, we can create the predictions from the shape-constrained GAM.

>>>>

This SCAM fits substantially better than a SCAM that only accounts for $\mu(t)$:

```{r, eval=TRUE}
m_mu <- scam(hr_est_95 ~ s(mu, bs = 'mpd', k = 5),
             family = Gamma('log'),
             weights = weight,
             data = tapir)
round(AIC(m, m_mu), 3)
```

We can now create the predictions from the shape-constrained GAM.
